\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewrote conclusion

	By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection based geometric framework. We have also established new theoretical results that support the use of projections for point forecast reconciliation. We show that projection of unbiased base forecasts onto the coherent subspace will always produce unbiased reconciled forecasts. Yet the projection-based reconciliation can be used to reconciled bias base forecasts after bias adjustments. Empirical results from the application of these methods to forecasting Australian domestic tourism flow show that reconciled forecast follows from bias-adjusted base improves the forecast accuracy and unbiased MinT reconciliation is outperforming.

	These new geometric interpretations of hierarchical forecast reconciliation facilitate extensions of the problem to a probabilistic framework. We leave this discussion into a different paper.

>>>>

	%By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection based geometric framework. We have also established new theoretical results that support the use of projections for point forecast reconciliation. We show that projection of unbiased base forecasts onto the coherent subspace will always produce unbiased reconciled forecasts. Yet the projection-based reconciliation can be used to reconciled bias base forecasts after bias adjustments. Empirical results from the application of these methods to forecasting Australian domestic tourism flow show that reconciled forecast follows from bias-adjusted base improves the forecast accuracy and unbiased MinT reconciliation is outperforming.

	Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods.  We have also provided evidence that reconciliation, particularly using the MinT method, can mitigate the effect of poor bias correction.  Our intention in proposing a geometric interpretation is also to provoke research into new areas.  We now discuss three such possibilites.

	First, it should be possible to extend to the concept of coherence to non-linear constraints.  In these cases the coherent space may need to be defined by a manifold.  Although much more challenging, it is still possible define reconciled forecasts in terms of projections onto a manifold.  Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether is may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.  Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework, an issue that we investigate in a separate paper.
